Map of France - only tests

### 2024-08-21 Map_FR.Rmd
A finer map of France

---
title: "Map of France"
output: pdf_document
date: "2024-08-20"
---

@@

>>>>

---
title: "Map of France - only tests"
output: pdf_document
date: "2024-08-20"
---

@@

```{r}
install.packages("cowplot")
library(cowplot)
```

```{r}
plot_grid(france_map)
```

ggplot() +
  geom_sf(data = france_map)+
  coord_sf(xlim = xlims, ylim = ylims, expand = FALSE) +
theme(
panel.grid.major = element_line(
    colour = "dodgerblue",
    linewidth = 0.5, linetype = "dotdash"
)
)
```

```{r}
library(maps)
data(franceMapEnv)
```

```{r}
map('france')
```
